Schramm-Loewner evolution in tricritical Ising model

### 2013-06-08 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Minor changes

Bolzmann weights are given by the expression
\begin{equation}
  \label{eq:5}
  W\left.\left(
    \begin{array}{cc}
      d & c\\
      a & b
    \end{array}\right| u \right)
= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
  \psi_c^{1/2}}{\psi_b} \delta_{bd},
\end{equation}
where
  \begin{equation}
    \label{eq:6}
    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
%%      \left.s_r(u)\right|_{\frac{\lambda}{\pi}\in \mathbb{Z}} =
%%      \lim_{\lambda'\to \lambda} \frac{\sin(r \lambda'
%%        +(\lambda'-\lambda)u)}{\sin \lambda'}
  \end{equation}
We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
The isotropic case $u=\lambda/2$ with boundary parameters
$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.

>>>>

Bolzmann  weights for the lattice faces are given by the expression
\begin{equation}
  \label{eq:5}
  W\left.\left(
    \begin{array}{cc}
      d & c\\
      a & b
    \end{array}\right| u \right)
= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
  \psi_c^{1/2}}{\psi_b} \delta_{bd},
\end{equation}
where
  \begin{equation}
    \label{eq:6}
    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
%%      \left.s_r(u)\right|_{\frac{\lambda}{\pi}\in \mathbb{Z}} =
%%      \lim_{\lambda'\to \lambda} \frac{\sin(r \lambda'
%%        +(\lambda'-\lambda)u)}{\sin \lambda'}
  \end{equation}

Bulk weights satisfy Yang-Baxter equation \cite{behrend2001integrable}
that leads to integrability of the model using transfer matrix
approach.

  We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
The isotropic case $u=\lambda/2$ with boundary parameters
$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.

Bolzmann weights for the lattice edges can differ from face weights.
Choice of these weights corresponds to different boundary conditions.
Conformally invariant boundary conditions for $A_4$ RSOS realization
of the tricritical Ising model were identified in
\cite{chim1996boundary}, boundary weights were listed in
\cite{behrend2001integrable}.

Behrend and Pearce use following labeling of boundary conditions for
rank $g$ model:
$\left\{(r,a)\ |\ r\in\{1,\dots,g-1\}, a\in {\cal G}\right\}$. For the
$(1,a)$ boundary condition boundary weights are given by the equation
\begin{equation}
  \label{eq:8}
  B^{1,a}\left.\left( c
    \begin{array}{ll}
      a & 1\\
      a & 1
    \end{array}\right| u, \xi \right)= \frac{s_0(\xi+u) s_1(\xi-u)
  \psi^{1/2}_c } {s_0(2\xi) \psi_a^{1/2}}
\end{equation}

So in the $(1, a)$ boundary condition the state of every alternate
boundary spin is fixed to be $a$, while each other boundary spin,
with state $c$ adjacent to $a$ on ${\cal G}$, is associated with a
weight proportional to $\psi_c^{1/2}$.

These boundary weights satisfy the boundary Yang-Baxter equation.
For the Ising and tricritical Ising models we limit ourselves with $r=1$
boundary states.

The weight of the spin configuration $C$ is equal to the product of
face weights and boundary weights:
\begin{equation}
  \label{eq:7}
  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mathrm{boundary
      faces}} B(b,C)
\end{equation}

\subsection{RSOS realization of Ising model}
\label{sec:rsos-real-ising}

For RSOS realization of Ising model we have:
\begin{eqnarray}
  \label{eq:10}
  2 \cos\lambda = \sqrt{2}\\
  \lambda=\frac{\pi}{4}\\
  \psi = (1,\sqrt{2},1)
\end{eqnarray}
So we obtain Boltzmann weights:
\begin{equation}
  \label{eq:9}
  \begin{array}{l}
  W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      1 & 2
    \end{array}\right| u \right) = \frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
  W\left.\left(
    \begin{array}{ll}
      1 & 2\\
      2 & 3
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
  W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      3 & 2
    \end{array}\right| u
\right)=\frac{1}{\sqrt{2}}\frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
  W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 1
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
  W\left.\left(
    \begin{array}{ll}
      3 & 2\\
      2 & 1
    \end{array}\right| u
\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
\end{array}
\end{equation}
